Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-11-01 paper.tex
Wrote command line construction

\documentclass{article}
\usepackage{minted}
\usepackage{pdfcomment}
\usepackage[margin=1in]{geometry}
\usepackage{lscape}
\usepackage[table]{xcolor}

\newcommand{\note}[2]{\pdfmargincomment[color=yellow,author=#1,open=true]{#2}}
\newcommand{\todo}[2]{\pdfmargincomment[color=red,author=#1,open=true]{#2}}

@@

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva,John Flavin, Pascal Girard, Krzysztof J. Gorgolewski, \\
        Nathaniel Kofalt, Pierre-Olivier Quirion, Pierre Rioux, Gunnar Schaeffer,\\
        Marc-\'Etienne Rousseau, Alan C. Evans}

@@

@@

@@

@@

% PSOM
% MICCAI Challenges 
% exports from Nipype
% SPM?
% BIDS Apps

>>>>

\documentclass{article}

%%%% Packages %%%%

\usepackage{minted} % Used for JSON highlighting
\usepackage{pdfcomment} % Used for notes and todos
\usepackage[margin=1in]{geometry} % Increases margins
\usepackage{lscape} % Used to put a section in landscape mode
\usepackage[table]{xcolor} % Color definitions
\usepackage{algorithm} % Algorithm float
\usepackage{algpseudocode} % Algorithmic environment

%%%% Commands %%%%

\newcommand{\note}[2]{\pdfmargincomment[color=yellow,author=#1,open=true]{#2}}
\newcommand{\todo}[2]{\pdfmargincomment[color=red,author=#1,open=true]{#2}}
\algrenewcommand{\algorithmiccomment}[1]{\# \textit{#1}} % so that comments in algorithms are preprended by '#' instead of a small right arrow

@@

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva,John Flavin, Pascal Girard, Krzysztof J. Gorgolewski, \\
        Charles G. Guttmann, Nathaniel Kofalt, Pierre-Olivier Quirion, Pierre Rioux,\\
        Gunnar Schaeffer, Marc-\'Etienne Rousseau, Alan C. Evans}

@@

At runtime, a value is assigned to all the mandatory and some of the
optional inputs. Inputs of type "String" may contain any string,
inputs of type "Number" must contain a string representing a number,
inputs of type "File" must contain a string representing a file path
(absolute or relative to the execution directory) and inputs of type
"Flag" must contain a boolean. When input is a list, the value
contains the concatenation of all strings in the list.

Algorithm~\ref{algo:command-line} shows how the application command
line is constructed from the application manifest and values entered
by the user. It substitutes all the value keys in the command line,
output path templates and configuration files, and writes the
configuration files.

\begin{algorithm}[htb]
\caption{Command-line construction}
\label{algo:command-line}
\begin{algorithmic}
  \State \Comment{Substitute input value keys in output path templates, configuration files and command line.}
  \For{\texttt{input} in \texttt{inputs}}
  \If{\texttt{input} has a \texttt{value-key}}
  \For{\texttt{output} in \texttt{outputs}}
  \State \texttt{stripped\_value} = \texttt{input\_value}
  \If{\texttt{input} type is \texttt{File}}
  \State In \texttt{stripped\_value}, remove  all elements in \texttt{path-template-stripped-extensions}.
  \EndIf
  \State In \texttt{path-template}, replace all occurrences of \texttt{value-key} by \texttt{stripped\_value}.
  \If{\texttt{output} has a \texttt{file-template}}
  \State In any line of \texttt{file-template}, replace all occurrences of \texttt{value-key} by \texttt{stripped\_value}.
  \EndIf
  \EndFor
  \State Prepend \texttt{command-line-flag} and \texttt{command-line-flag-separator} to \texttt{input\_value}.
  \State In \texttt{command-line}, replace all occurrences of \texttt{value-key} by \texttt{input\_value}.
  \EndIf
  \EndFor

  \State \Comment{Substitute output value keys in configuration files and command line.}
  \For{\texttt{output} in \texttt{outputs}}
  \If{\texttt{output} has a \texttt{value-key}}
  \For{\texttt{output} in \texttt{outputs}}
  \If{\texttt{output} has a \texttt{file-template}}
  \State In any line of \texttt{file-template}, replace all occurrences of \texttt{value-key} by \texttt{path-template}.
  \State \Comment{Input \texttt{value-key} have been substituted in \texttt{path-template} previously.}
  \EndIf
  \EndFor
  \State Prepend \texttt{command-line-flag} and \texttt{command-line-flag-separator} to \texttt{path-template}.
  \State In \texttt{command-line}, replace all occurrences of \texttt{value-key} by \texttt{path-template}.
  \EndIf
  \EndFor

  \State \Comment{Write all configuration files.}
  \For{\texttt{output} in \texttt{outputs}}
  \If{\texttt{output} has a \texttt{file-template}}
  \State Write \texttt{file-template} in \texttt{path-template}
  \State \Comment{Value keys have been substituted in \texttt{file-template} previously.}
  \EndIf
  \EndFor

\end{algorithmic}
\end{algorithm}

@@

% SPM?
% BIDS Apps

@@

\paragraph{SPINE}

@@
